Competing Bandits Overview

### 2018-05-08 analysis_code/agents_table.Rmd
add additional plots to the overview

#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_large_horizon_3_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000, 15000)
priors <- as.list(unique(dat['Prior']))$Prior

>>>>

#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_multiple_haystack_2_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000, 15000)
priors <- as.list(unique(dat['Prior']))$Prior

### 2018-05-08 analysis_code/tournament_table.Rmd
add additional plots to the overview

#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/full_tournament_raw_results.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_test_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- algs
        rownames(results) <- algs
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

>>>>

#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_reputation_window_raw.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_greedy_thompson_2_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(3000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "ThompsonStaticGreedy", "ThompsonDynamicGreedy")
alg_names <- c("Thompson Sampling", "Thompson Static Greedy", "Thompson Dynamci Greedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- alg_names
        rownames(results) <- alg_names
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

### 2018-05-08 overview/overview.tex
add additional plots to the overview

Considered $K = 3$, $Memory = 100$ (unless otherwise noted) \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Uniform: Draw the mean rewards for the arms from [0.25, 0.75]
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means.
\item Needle-in-haystack
\begin{enumerate}
\item High - 2 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon=0.05$
\end{enumerate}
\textbf{Agent Algorithms considered}:
\begin{enumerate}
\item HardMax
\item HardMaxWithRandom ($\epsilon = 0.05$)
\item SoftMax ($\alpha = 30$)
\end{enumerate}
\textbf{Memory Sizes}
\begin{enumerate}
\item 100
\end{enumerate}
\pagebreak
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
\State Generate true distribution from $p$ (except for needle-in-haystack, just use $p$ itself)
\State Generate $T \times K$ realizations for the arms 
	\For{Each agent algorithm $agent alg$}
		\For{Each principal algorithm pair $principalalg1$, $principalalg2$}
			\For{$N$ simulations}

@@

\section*{Results}

First, let's look at the preliminary simulation results on the instances we considered. What is plotted here is the reputation score for a memory size of $100$ for each of the priors and each of the algorithms:

@@

The first set of results we will consider are $X = 0$ and $k = 5$ so that there is simultaneous entry and only a small cold start. Recall to read the tables: \\
\begin{enumerate}
\item In bold is the average market share for principal 1 and with a 95\% confidence interval
\item The var term is the variance of the market shares
\item The ``share" line means the \% of simulations that ended up with one principal getting more than 90\% of the market.
\end{enumerate}

@@

@@

The conjecture for HMR and SM seems to be consistent with the data generated from the simulation. However, what is going on with HardMax appears confusing. To get some more evidence for the original conjecture, we re-run simulations but track market share over time. In most cases, we get evidence of this and the vast majority of market shares over time look as follows:

@@

As a comparison, what do the trajectories for the HardMaxWithRandom agent response functions look like? Haven't dug too deeply into the data for these simulations, but here is a sample one (ThompsonSampling vs DEG - plotted market share is for ThompsonSampling) that is similar to many in those that I have looked at: \\
\includegraphics[scale=0.25]{hmr_over_time} \\
\textbf{Puzzles}: Inconsistent with this interpretation of the HardMax results is the result for the Heavy Tail prior. Why does Thompson Sampling do so poorly! Looking at the reputation plots we see that in the early rounds there is very little difference between the algorithms but Thompson Sampling still does better, even if only slightly. Thus, it's kind of confusing as to what is actually going on. Perhaps worth looking more closely at some of the trajectory plots for this prior.\\

In general, the conjecture that differences in algorithm performance in early rounds is important for determining results in HardMax and differences in algorithm performance for large $T$ is important for determining results in HardMaxWithRandom and SoftMax seems to be roughly validated.

>>>>

Considered $K = 3$, $Memory = 100$ (unless otherwise noted) \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Uniform: Draw the mean rewards for the arms from [0.25, 0.75]
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means.
\item Needle-in-haystack
\begin{enumerate}
\item High - 2 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon=0.05$
\end{enumerate}
\textbf{Agent Algorithms considered}:
\begin{enumerate}
\item HardMax
\item HardMaxWithRandom ($\epsilon = 0.05$)
\item SoftMax ($\alpha = 30$)
\end{enumerate}
\textbf{Memory Sizes}
\begin{enumerate}
\item 100
\end{enumerate}
\pagebreak
\textbf{Competing Bandits Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
\State Generate true distribution from $p$ (except for needle-in-haystack, just use $p$ itself)
\State Generate $T \times K$ realizations for the arms 
	\For{Each agent algorithm $agent alg$}
		\For{Each principal algorithm pair $principalalg1$, $principalalg2$}
			\For{$N$ simulations}

@@

\section*{Preliminary Calibration}

First, let's look at the preliminary simulation results on the instances we considered. In these simulations we simply run the selected bandit algorithm on the selected prior (no competition).  What is plotted here is the reputation score for a memory size of $100$ for each of the priors and each of the algorithms (recall that reputation score is the average of the last 100 observations):

@@

One thing which may be problematic with these plots is that for Heavy Tail and Uniform the means for the instances are randomly drawn for each simulation but these plots just take averages over all of the simulations.

Some additional preliminary calibration plots. These plots show the \% of simulations over $N=200$ that identified the best arm over time (based on looking at the posterior distributions at a given time): \\
\includegraphics[scale=0.5]{"needle_in_haystack_best_arm_ident"} \\
\includegraphics[scale=0.5]{"heavy_tail_best_arm_ident"} \\
\includegraphics[scale=0.5]{"uniform_best_arm_identification"}

@@

The first set of results we will consider are $X = 0$ and $k = 5$ so that there is simultaneous entry. Recall to read the tables: \\
\begin{enumerate}
\item In bold is the average market share for principal 1 and with a 95\% confidence interval
\item The var term is the variance of the market shares
\item The ``share" line means the \% of simulations that ended up with one principal getting more than 90\% of the market.
\end{enumerate}

@@

The conjecture for HMR and SM seems to be consistent with the data generated from the simulation (the one exception seems to be HeavyTail for BG vs BEG - more on this later). However, what is going on with HardMax appears confusing. To get some more evidence for the original conjecture, we re-run simulations but track market share over time. In most cases, we get evidence of this and the vast majority of market shares over time look as follows:

@@

As a comparison, what do the trajectories for the HardMaxWithRandom agent response functions look like? Haven't dug too deeply into the data for these simulations, but here is a sample one (ThompsonSampling vs DEG - plotted market share is for ThompsonSampling) that is similar to many in those that I have looked at: \\
\includegraphics[scale=0.25]{hmr_over_time} \\
\textbf{Puzzles}: Inconsistent with this interpretation of the HardMax results is the result for the Heavy Tail prior. Why does Thompson Sampling do so poorly! Looking at the reputation plots we see that in the early rounds there is very little difference between the algorithms but Thompson Sampling still does better, even if only slightly. Thus, it's kind of confusing as to what is actually going on. Perhaps worth looking more closely at some of the trajectory plots for this prior. As well, Bayesian Greedy seems to beat Bayesian Epsilon Greedy on this prior even when there is randomness in the agent response model which seems puzzling given the preliminary plots. \\

In general, the conjecture that differences in algorithm performance in early rounds is important for determining results in HardMax and differences in algorithm performance for large $T$ is important for determining results in HardMaxWithRandom and SoftMax seems to be roughly validated (but there are some cases we need to think more about what is happening).
